Embeddings and Attention in Predictive Modeling

### 2022-03-27 manuscript/manuscript.Rmd
elaborate on glm with embeddings

Since we only have a few parameters in this model, we exhibit the full list of fitted coefficients in Table \@ref(tab:glm2).

>>>>

Since we only have a few parameters in this model, we exhibit the full list of fitted coefficients in Table \@ref(tab:glm2). 
For each categorical variable, there is only one coefficient estimate. This is because each categorical variable has been replaced by a
single scalar value, so we treat it as if it were any other continuous predictor.

One interesting ramification of our choice of embedding dimension of 1 in this example is that we can compute the "implied relativities"
of the factor levels in the new GLM. Since each level corresponds to a unique scalar value, we can obtain its contribution to the
linear predictor by multiplying by the coefficient estimate of the variable. For example, multiplying the estimate of -0.075 for `occupancy_type` in
Table \@ref(tab:glm2) by each value in Table \@ref(tab:embeddings-flood-zone), we obtain the unnormalized contributions of each level, which can
then be exponentiated and normalized with respect to the base level `Single family residence` in order to obtain the implied relativities,
which could then be compared with the first GLM's output in Table \@ref(tab:relativities).
